Wind Veer and Speed in Turbulent Ekman Flow - Part 1: Scaling analysis and universal profile model

### 2024-10-10 write1/manuscript.tex
added figure Caption for comparison with K-Theorty

\subsection{Comparison with other theories}
%%% VAN DRIEST SCALING
An alternative approach that considers viscous effects close to the surface is the van-Driest scaling \citep{vandriest:JOT1956}, 
where an exponential damping of Prandtl's mixing length is considered near the wall to yield 
\begin{align}
  \frac{\p u^+}{\p y^+} = \frac{2}{ 1+ \sqrt{1+\left(2\kappa y^+\right)^2 (1-\exp\left[-y^+\right])}};
\end{align}
the spanwise component is zero as no rotational effects are considered. 
%
Comparing our proposed formulation (Fig.~\ref{fig:vanDriest}) for the stream-wise velocity in the inner layer to  \citeauthor{vandriest:JOT1956}'s formulation 
yields later convergence of the velocity onto the logarithmic profile while, over all, it serves as an excellent model of the streamwise 
velocity component:
% 
Notable deviations (on the order of few percent) only occur in the region $10 < z^+ < 30$, 
where the velocity transitions from the linear to the logarithmic profile. 
\begin{figure}
  \centerline{\includegraphics[width=0.66\textwidth]{../plot/vanDriest_profile.png}}
  \caption{Near-wall velocity profile according to the 
    van-Driest scaling (blue, solid) in comparison with 
    the present model (red, dashed), 
    the viscous law of the wall (orange dashed), and 
    the logarithmic law (green, solid)} 
  \label{fig:vanDriest}
\end{figure}

@@

%ETLING MODEL 
A two-layer model consolidating both the logartihmic and Ekman layer can be obtained following the arguments by \cite{etling:2008}, cf. \cite{emeis:2018}. Given a surface veering and a matching height (extent of the logarithmic layer), a formulation for the velocity profile across both the logarithmic and the outer layer is obtained. A comparison using the surface veering based on our model and a matching height of $z_\text{prandtl}=0.05\delta$, which gives better results than the matching height of $0.1\delta$ suggested by \cite{etling:2008}, is shown in Fig.~\ref{fig:etling}. 
% 
The overall shape of velocity magnitude is matched apart from the viscous and buffer layer (cf. Fig.~\ref{fig:etling}b) that is neglected by the two-layer model. However, quantitative departures on the order of 10\% occur across the inner layer: it turns out that the non-rotating profile, of the two-layer model in the logarithmic region yields too low overall velocity as the spanwise component contributes to the velocity across the inner layer. 
% 
Deviations also occur with respect to wind direction; despite the rather low matching height, a substantial fraction of the rotation occurs within the lower part of the ABL and about 20\% of the wind veer is not captured by the two-layer model. 
% 
As the overall veer is given, the non-captured veer close to the surface is then compensated across the logarithmic layer. In the upper part of the boundary layer, both profiles match well. 
% 
\begin{figure}
  \textbf{(a)\hspace{0.48\textwidth}(b)}\\
  \includegraphics[width=0.5\textwidth]{../plot/etling_direction_1.pdf} 
  \includegraphics[width=0.5\textwidth]{../plot/etling_magnitude_1.pdf}
  \caption{Comparison of the DNS data (dashed lines) with the two-layer model proposed by Etling (solid lines) for different Reynolds number. Left panel shows the relative wind veer, right panel shows the velocity magnitude. The etling model is calibrated by the surface veer from the DNS and roughness parameter for the Etling model is chosen according to the correction factor $\exp{\kappa A}$ such that the total veer and velocity magnitude agree. DNS profile in the buffer layer, defined here as $z^+<30$ are shown as opaque dashed lines as the two-layer model does not consider viscous effects.}
  \label{fig:etling} 
\end{figure}

\begin{figure}
  \textbf{(a)\hspace{0.48\textwidth}(b)}\\
  \includegraphics[width=0.5\textwidth]{../plot/stress_rotation.pdf}
  \includegraphics[width=0.5\textwidth]{../plot/misalignment.pdf} 
  \caption{} 
  \label{fig:alignment}
\end{figure}
outlined in 
\textbf{Compare} Gryning (2007); highlight explicit knowledge on veering-profile $\rightarrow$ directional sheer;

>>>>

\subsection{Comparison with other theories}
%%% VAN DRIEST SCALING
\begin{figure}
  \centerline{\includegraphics[width=0.66\textwidth]{../plot/vanDriest_profile.png}}
  \caption{Near-wall velocity profile according to the 
    van-Driest scaling (blue, solid) in comparison with 
    the present model (red, dashed), 
    the viscous law of the wall (orange dashed), and 
    the logarithmic law (green, solid)} 
  \label{fig:vanDriest}
\end{figure}  An alternative approach that considers viscous effects close to the surface is the van-Driest scaling \citep{vandriest:JOT1956}, 
where an exponential damping of Prandtl's mixing length is considered near the wall to yield 
\begin{align}
  \frac{\p u^+}{\p y^+} = \frac{2}{ 1+ \sqrt{1+\left(2\kappa y^+\right)^2 (1-\exp\left[-y^+\right])}};
\end{align}
the spanwise component is zero as no rotational effects are considered. 
%
Comparing our proposed formulation (Fig.~\ref{fig:vanDriest}) for the stream-wise velocity in the inner layer to  \citeauthor{vandriest:JOT1956}'s formulation 
yields later convergence of the velocity onto the logarithmic profile while, over all, it serves as an excellent model of the streamwise 
velocity component:
% 
Notable deviations (on the order of few percent) only occur in the region $10 < z^+ < 30$, 
where the velocity transitions from the linear to the logarithmic profile.

@@

%ETLING MODEL 
\begin{figure}
  \textbf{(a)\hspace{0.48\textwidth}(b)}\\
  \includegraphics[width=0.5\textwidth]{../plot/etling_direction_1.pdf} 
  \includegraphics[width=0.5\textwidth]{../plot/etling_magnitude_1.pdf}
  \caption{Comparison of the DNS data (dashed lines) with the two-layer model proposed by Etling (solid lines) for different Reynolds number. Left panel shows the relative wind veer, right panel shows the velocity magnitude. The etling model is calibrated by the surface veer from the DNS and roughness parameter for the Etling model is chosen according to the correction factor $\exp{\kappa A}$ such that the total veer and velocity magnitude agree. DNS profile in the buffer layer, defined here as $z^+<30$ are shown as opaque dashed lines as the two-layer model does not consider viscous effects.}
  \label{fig:etling} 
\end{figure}A two-layer model consolidating both the logartihmic and Ekman layer can be obtained following the arguments by \cite{etling:2008}, cf. \cite{emeis:2018}. Given a surface veering and a matching height (extent of the logarithmic layer), a formulation for the velocity profile across both the logarithmic and the outer layer is obtained. A comparison using the surface veering based on our model and a matching height of $z_\text{prandtl}=0.05\delta$, which gives better results than the matching height of $0.1\delta$ suggested by \cite{etling:2008}, is shown in Fig.~\ref{fig:etling}. 
% 
The overall shape of velocity magnitude is matched apart from the viscous and buffer layer (cf. Fig.~\ref{fig:etling}b) that is neglected by the two-layer model. However, quantitative departures on the order of 10\% occur across the inner layer: it turns out that the non-rotating profile, of the two-layer model in the logarithmic region yields too low overall velocity as the spanwise component contributes to the velocity across the inner layer. 
% 
Deviations also occur with respect to wind direction; despite the rather low matching height, a substantial fraction of the rotation occurs within the lower part of the ABL and about 20\% of the wind veer is not captured by the two-layer model. 
% 
As the overall veer is given, the non-captured veer close to the surface is then compensated across the logarithmic layer. In the upper part of the boundary layer, both profiles match well. 
%

\begin{figure}
  \textbf{(a)\hspace{0.48\textwidth}(b)}\\
  \includegraphics[width=0.5\textwidth]{../plot/stress_rotation.pdf}
  \includegraphics[width=0.5\textwidth]{../plot/misalignment.pdf} 
  \caption{Panel \textbf{(a)} shows the wind direction (DD) as thick dashed lines and the direction of stress relative to DD as thin solid lines, both according to our profile model. The direction of the negative flux vector $(\overline{u'w'},\overline{v'w'})$ based on DNS data is shown as a dotted line. In panel \textbf{(b)}, we plot the misalignment, i.e. the angle, between the flux vector and the shear vector, where the shear vector is defined accordingly as $(\p_z U, \p_z V)$.} 
  \label{fig:alignment}
\end{figure}
outlined in 
\textbf{Compare} Gryning (2007); highlight explicit knowledge on veering-profile $\rightarrow$ directional sheer;
